---
title: "preprocessing omics on lung cancer"
author: "sara yusuf"
date: "2024-03-01"
output: html_document
---

    Dataset Description

 multiomics data analysis WITH MOFA  using Lung squamous cell carcinoma dataset.
 21792 genes 11111 protien and 16478 Calculated beta values mapped to genome from 108 samples with a confirmed diagnosis with LSCC and 94 healthy individuals.
 THREE types of data were used : protiens , genes , and mythelation data

    dataset source

"https://linkedomics.org/data_download/CPTAC-LSCC/"

    Citation
Suhas V Vasaikar, Peter Straub, Jing Wang, Bing Zhang, LinkedOmics: analyzing multi-omics data within and across 32 cancer types, Nucleic Acids Research, Volume 46, Issue D1, 4 January 2018, Pages D956–D963.https://doi.org/10.1093/nar/gkx1090

```{r}

library(magrittr)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(vegan)
library(devtools)
library(data.table)
library(impute)
```


```{r}
#if (!requireNamespace("BiocManager", quietly = TRUE))
#    install.packages("BiocManager")

#BiocManager::install("MOFA2")
library(MOFA2)
```


```{r}
transciptome.tumor  = read.csv("COMP_BIO/moda/HS_CPTAC_LSCC_2020_rnaseq_uq_fpkm_log2_NArm_TUMOR.cct", row.names = 1 ,
sep ="\t")
transciptome.normal = read.csv("COMP_BIO/moda/HS_CPTAC_LSCC_2020_methylation_mean_gene_tumor.cct", row.names = 1 ,
sep ="\t")

```


```{r}
proteome.tumor  = read.csv("COMP_BIO/moda/proteomics/lung cancer proteome tumor.cct", row.names = 1 ,
sep ="\t")
proteome.normal = read.csv("COMP_BIO/moda/proteomics/lung cancer proteome normal.cct", row.names = 1 ,
sep ="\t") 
```


```{r}
methylation.tumor  = read.csv("COMP_BIO/moda/HS_CPTAC_LSCC_2020_methylation_mean_gene_tumor.cct", row.names = 1 ,
sep ="\t")
methylation.normal = read.csv("COMP_BIO/moda/HS_CPTAC_LSCC_2020_methylation_mean_gene_normal.cct", row.names = 1 ,
sep ="\t")
```



```{r}
colnames(transciptome.normal)= paste0("sampleN",1: length(transciptome.normal))
colnames(transciptome.tumor) = paste0("sampleT" ,1: length(transciptome.tumor))
colnames(proteome.normal)    = paste0("sampleN" ,1: length(proteome.normal))
colnames(proteome.tumor)     = paste0("sampleT" ,1: length(proteome.tumor))
colnames(methylation.normal) = paste0("sampleN" ,1: length(methylation.normal))
colnames(methylation.tumor)  = paste0("sampleT" ,1: length(methylation.tumor))
```


```{r}
clinical.n = read.csv("COMP_BIO/moda/proteomics/lung cancer clinical normal.tsi" ,row.names = 1 ,
sep ="\t" )
clinical.t= read.csv("COMP_BIO/moda/proteomics/lung cancer clinical tumor" ,row.names = 1 ,
sep ="\t")

clinical.t = clinical.t[ -1 , -2]
clinical.n = clinical.n[ -1 ,   ]

```


```{r}
rownames(clinical.n)= paste0("sampleN",1: dim(clinical.n)[1])
rownames(clinical.t) = paste0("sampleT" ,1: dim(clinical.t)[1])
```


```{r}
all(rownames(transciptome.normal) %in% rownames(transciptome.tumor))
```


```{r}
transciptome.tumor  = transciptome.tumor %>% data.frame %>% rownames_to_column("id")
transciptome.normal = transciptome.normal%>% data.frame %>% rownames_to_column("id")
proteome.normal     = proteome.normal    %>% data.frame %>% rownames_to_column("id")
proteome.tumor      = proteome.tumor     %>% data.frame %>% rownames_to_column("id")
methylation.normal  = methylation.normal %>% data.frame %>% rownames_to_column("id")
methylation.tumor   = methylation.tumor  %>% data.frame %>% rownames_to_column("id")

```


```{r}
transcriptome = transciptome.normal%>%
  inner_join( . , transciptome.tumor , by = "id")
```


```{r}
proteome = proteome.normal%>%
  inner_join( . , proteome.tumor , by = "id")
```


```{r}
methylation = methylation.normal %>%
  inner_join( . , methylation.tumor , by = "id")
```


```{r}
dim(transcriptome)
sum(is.na(transcriptome))
```
```{r}
trans.t = setNames(data.frame(t(transcriptome[,-1])), transcriptome[,1])
```


```{r}
var = apply( trans.t , 2 ,var , na.rm = T )
trans.var = trans.t[, !(var == 0 | is.na(var))]
trans.var = as.matrix(trans.var)
```

```{r}
h=hist((apply(is.na(trans.var), 2, sum)/nrow(trans.var) ) *100,breaks=10,
main="QC",
xlab="percentage of missingness")
text(h$mids,h$counts,labels=h$counts, adj=c(0.5, -0.5))
abline(v = 70)
```


```{r}
keep = apply(is.na(trans.var), 2, sum)/nrow(trans.var) <0.7

```


```{r}


trans.filt=trans.var[,keep]
dim(trans.var)
dim(trans.filt)
trans.imputed = impute.knn(trans.filt,k=10)$data
dim(trans.imputed)

sum(is.na(trans.imputed))
trans.logged = log2(trans.imputed + 1)
trans.scaled = scale(trans.logged, scale = T)
```




```{r}
par(mfrow=c(1,3))
plot(density(apply(trans.imputed, 2, mean, na.rm = TRUE)),main='befor log2')
plot(density(apply(trans.logged, 2, mean, na.rm = TRUE)),main='after log2')
plot(density(apply(trans.scaled, 2, mean, na.rm = TRUE)),main='after  scaling')
```


```{r}
par(mar = c(8,5,2,2),mfrow=c(1,3))
boxplot(t(trans.imputed[1:20,]), main="Before log2" ,horizontal=T,las=2,col = "blue")
boxplot(t(trans.logged[1:20,]), main="After log2" ,horizontal=T,las=2,col = "blue")
boxplot(t(trans.scaled[1:20,]), main="After scaling " ,horizontal=T,las=2,col = "orange")

```

```{r}

proteome.t = setNames(data.frame(t(proteome[,-1])), proteome[,1])
```


```{r}
var = apply( proteome.t , 2 ,var , na.rm = T )
prot.var = proteome.t[, !(var == 0 | is.na(var))]
prot.var = as.matrix(prot.var)
```

```{r}
h=hist((apply(is.na(prot.var), 2, sum)/nrow(prot.var) ) *100,breaks=10,
main="QC",
xlab="percentage of missingness")
text(h$mids,h$counts,labels=h$counts, adj=c(0.5, -0.5))
abline(v = 50)
```


```{r}
keep = apply(is.na(prot.var), 2, sum)/nrow(prot.var) <0.5

```


```{r}
prot.filt=prot.var[,keep]
dim(trans.var)
dim(prot.filt)
prot.imputed = impute.knn(prot.filt,k=10)$data
dim(prot.imputed)

sum(is.na(prot.imputed))
prot.scaled = scale(prot.imputed, scale = T)
sum(is.na(prot.scaled))
```


```{r}
par(mfrow=c(1,3))
plot(density(apply(prot.imputed, 2, mean, na.rm = TRUE)),main='befor scaling')
plot(density(apply(prot.scaled, 2, mean, na.rm = TRUE)),main='after  scaling')
```


```{r}
par(mar = c(8,5,2,2),mfrow=c(1,3))
boxplot(t(prot.imputed[1:20,]), main="Before scaling" ,horizontal=T,las=2,col = "blue")
boxplot(t(prot.scaled[1:20,]), main="After scaling " ,horizontal=T,las=2,col = "orange")


```


```{r}
meth.t = setNames(data.frame(t(methylation[,-1])), methylation[,1])
```


```{r}
var = apply( meth.t , 2 ,var , na.rm = T )
meth.var = meth.t[, !(var == 0 | is.na(var))]
meth.var = as.matrix(meth.var)
```

```{r}
h=hist((apply(is.na(meth.var), 2, sum)/nrow(meth.var) ) *100,breaks=10,
main="QC",
xlab="percentage of missingness")
text(h$mids,h$counts,labels=h$counts, adj=c(0.5, -0.5))
abline(v = 70)
```


```{r}
keep = apply(is.na(meth.var), 2, sum)/nrow(meth.var) <0.7

```


```{r}

meth.filt=meth.var[,keep]
dim(meth.var)
dim(trans.filt)
meth.imputed = impute.knn(meth.filt,k=10)$data
dim(meth.imputed)

sum(is.na(meth.imputed))
meth.logged = log2(meth.imputed + 1)
meth.scaled = scale(meth.logged, scale = T)
sum(is.na(meth.scaled))
```




```{r}
par(mfrow=c(1,3))
plot(density(apply(meth.imputed, 2, mean, na.rm = TRUE)),main='befor log2')
plot(density(apply(meth.logged, 2, mean, na.rm = TRUE)),main='after log2')
plot(density(apply(meth.scaled, 2, mean, na.rm = TRUE)),main='after  scaling')
```


```{r}
par(mar = c(8,5,2,2),mfrow=c(1,3))
boxplot(t(meth.imputed[1:20,]), main="Before log2" ,horizontal=T,las=2,col = "blue")
boxplot(t(meth.logged[1:20,]), main="After log2" ,horizontal=T,las=2,col = "blue")
boxplot(t(meth.scaled[1:20,]), main="After scaling " ,horizontal=T,las=2,col = "orange")

```


```{r}
dim(meth.scaled)
dim(prot.scaled)
dim(trans.scaled)
```


```{r}
methylation.matrix = t(meth.scaled)
protien.matrix = t(prot.scaled)
rna.matrix = t(trans.scaled)

```

```{r}
clinical.n = clinical.n%>%
  mutate(condition = "normal")

clinical.t =clinical.t%>%
  mutate(condition = "tumor")
```


```{r}
meta = rbind(clinical.n , clinical.t)
```


```{r}
#write.csv(methylation.matrix , "COMP_BIO/moda/meth")
#write.csv(protien.matrix , "COMP_BIO/moda/prot")
#write.csv(rna.matrix , "COMP_BIO/moda/rna")
#write.csv(meta , "meta")


```


```{r}
library(corrplot)
library(RColorBrewer)
M = cor(trans.scaled[,20:40])
corrplot(M, type="upper", order="hclust" )

```
```{r}
rownames(trans.scaled) = trans.scaled[ ,1]
```



```{r}
i_col = intersect(rownames(meta), rownames(trans.scaled))

```


```{r}
trans.scaled  = trans.scaled [  i_col ,]
meta = meta[ i_col , ]

```

```{r}

```



```{r}
df_pca = prcomp(trans.scaled)
df_out = as.data.frame(df_pca$x)
ggplot(df_out,aes(x=PC1 ,y=PC2 ,color = clinical$condition, shape=clinical$condition))+
geom_point()+ggtitle("")+labs(color='')
```



```{r}
kmeans2 = kmeans(rna.matrix , centers = 2, nstart = 25)
kmeans3 = kmeans(rna.matrix , centers = 3, nstart = 25)  
kmeans4 = kmeans(rna.matrix , centers = 4, nstart = 25)  
kmeans5 = kmeans(rna.matrix , centers = 5, nstart = 25)  
 #Comparing the Plots
plot1 = fviz_cluster(kmeans2, geom = "point", data = data.scaled) + ggtitle("k = 2")
plot2 = fviz_cluster(kmeans3, geom = "point", data = data.scaled) + ggtitle("k = 3")
plot3 = fviz_cluster(kmeans4, geom = "point", data = data.scaled) + ggtitle("k = 4")
plot4 = fviz_cluster(kmeans5, geom = "point", data = data.scaled) + ggtitle("k = 5")
grid.arrange(plot1, plot2, plot3, plot4, nrow = 2)

```


```{r}
plot(kmeans2, data=data.scaled)
```


```{r}
table(clinical$condition, kmeans2$cluster)

```


```{r}
fviz_nbclust(data.scaled, kmeans, method = "silhouette")

```


```{r}
fviz_nbclust(data.scaled, kmeans, method = "wss")

```


```{r}
options(repr.plot.width = 50, repr.plot.height = 10)

d   = dist(data.scaled, method = "euclidean") 
fit = hclust(d, method="ward.D" )
plot(fit , hang = -10) 
groups = cutree(fit, k=2) 
rect.hclust(fit, k=2, border="green" )
```


```{r}
library(limma)
type   = as.character(clinical$condition)

design = model.matrix(~0+factor(type))

colnames(design) = levels(factor(type))



contrast = makeContrasts( tumor - normal,levels=design)
fit      = lmFit(as.matrix(t(data.scaled)), design)
fit2     = contrasts.fit(fit, contrast)
fit2     = eBayes(fit2)

```


```{r}
res = topTable(fit2, adjust.method='fdr', number=99999999 , p.value = .05 , coef = 1)
dim(res)
head(res)
```


```{r}
res$diffexpressed = "NO"
res$diffexpressed[res$logFC > 0 & res$P.Value < 0.05] = "UP"
res$diffexpressed[res$logFC < -0.6 & res$P.Value < 0.05] = "DOWN"
     
```

```{r}
des_reg = res %>% filter( P.Value < 0.05 ) %>% arrange (desc = F) %>% rownames %>% head(100)
```



```{r}
library(EnhancedVolcano)
EnhancedVolcano(res,
    lab = rownames(res),
    x = 'logFC',
    y = 'adj.P.Val',
    title = 'cancer versus healthy',
    pCutoff = 10e-32,
    FCcutoff =1,
    pointSize = 3.0,
    labSize = 2.0)
```
```{r}
top_table = data.scaled[ , des_reg]
```


```{r}
set.seed(000)
mycolors= rep("navy",dim(matched.clinical)[1])
mycolors[which(matched.clinical=="tumor")]="purple"

column_ha = HeatmapAnnotation(Sample_type= clinical$condition)
Heatmap(t(top_table), name = "top", top_annotation = column_ha)
Heatmap(t(top_table), name = "top", top_annotation = column_ha, row_names_gp = gpar(fontsize = 1), column_names_gp = gpar(fontsize = .5, mycolors))
```

```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

