---
title: "mofa on lung cancer"
author: "sara yusuf"
date: "2024-03-01"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

# libraries loading


```{r}
library(htmltools)
library(BiocManager)
library(basilisk)
library(magrittr)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(vegan)
library(data.table)
library(MOFA2)
library(tibble)



```
 #reading the rna, protein ,mirna and methylation matrices that were already processed plus the metadata matrix.

```{r}
# rna = read.csv("c:/Users/saraa/Desktop/COMP_BIO/moda/mofa on lung ca/rna" ,row.names = 1, header = T )
# meth = read.csv("c:/Users/saraa/Desktop/COMP_BIO/moda/mofa on lung ca/meth",row.names = 1, header = T )
# prot = read.csv("c:/Users/saraa/Desktop/COMP_BIO/moda/mofa on lung ca/prot",row.names = 1, header = T )
# mirna = read.csv("c:/Users/saraa/Desktop/COMP_BIO/moda/mirna/miRNA.scaled" , row.names = 1 , header = T)
# meta = read.csv("c:/Users/saraa/Desktop/COMP_BIO/moda/mofa on lung ca/meta",row.names = 1, header = T )

```

#now some exploration and matching to unify the common samples between omics data 




```{r}
# rna = as.matrix(rna)
# meth = as.matrix(meth)
# prot = as.matrix(prot)
# mirna = as.matrix(mirna)

```



```{r}
#i_col = intersect(colnames(mirna), colnames(meth))
```


```{r}
# rna_x  =  rna  [ , i_col]
# mirna_x=  mirna[ , i_col]
# meth_x =  meth [ , i_col]
# prot_x =  prot [ , i_col]
# meta_x =  meta [i_col , ]
```


```{r}
# write.csv( rna_x , "rna_matched")
# write.csv( mirna_x , "mirna_matched")
# write.csv( prot_x , "prot_matched")
# write.csv( meth_x , "meth_matched")
# write.csv( meta_x , "meta_matched")


```


```{r}
rna = read.csv("C:/Users/saraa/Desktop/rna_matched" , header = T , row.names = 1)
mirna = read.csv("C:/Users/saraa/Desktop/mirna_matched", header = T , row.names = 1)
prot = read.csv("C:/Users/saraa/Desktop/prot_matched", header = T , row.names = 1)
meth = read.csv("C:/Users/saraa/Desktop/meth_matched", header = T , row.names = 1)
meta = read.csv("C:/Users/saraa/Desktop/meta_matched", header = T , row.names = 1)

```


```{r}
dim(rna)
dim(meth)
dim(prot)
dim(mirna)

```

```{r}
all(colnames(rna) == colnames(meth))
all(colnames(rna) == colnames(prot))
all(colnames(mirna) == colnames(prot))
all(colnames(rna) == rownames(meta))

```
#we need to compile all data into a list of matrices 

```{r}
data = list(rna = rna , meth = meth , prot = prot , mirna = mirna)
``` 

```{r}
lapply(data,dim)
```
#moving to preparing the MOFA object to fit the model

```{r}

#MOFAobject = create_mofa(data)



#plot_data_overview(MOFAobject)


#data_opts = get_default_data_options(MOFAobject)
#data_opts

#model_opts = get_default_model_options(MOFAobject)
#model_opts$num_factors = 10

#model_opts


#train_opts = get_default_training_options(MOFAobject )
#train_opts$convergence_mode = "slow"

#train_opts
##MOFAobject = prepare_mofa(
#  object = MOFAobject,
#  data_options = data_opts,
#  model_options = model_opts,
#  training_options = train_opts
```


```{r}
#outfile = file.path(getwd(),"model.hdf5")
#MOFAobject.trained = run_mofa(MOFAobject, outfile , use_basilisk = T)
```

```{r}
MOFAobject.trained = load_model("C:/Users/saraa/Desktop/COMP_BIO/moda/mofa on lung ca/model1.hdf5")
```




#after fitting the model ... some exploration and visualization

```{r}
names(MOFAobject.trained@data)

```


```{r}
dim(MOFAobject.trained@data$rna$group1)

```


```{r}
names(MOFAobject.trained@expectations)

```


```{r}
dim(MOFAobject.trained@expectations$W$rna)
```
# we need to familiarize our model with the metadata in order to start comparison 


```{r}
meta = meta%>%
  rownames_to_column("sample")
```

```{r}

 stopifnot(all(sort(meta$sample) == sort(unlist(samples_names(MOFAobject.trained)))))
```


```{r}
samples_metadata(MOFAobject.trained) = meta

```

```{r}
head(MOFAobject.trained@cache$variance_explained$r2_total[[1]]) # group 1

```


```{r}
head(MOFAobject.trained@cache$variance_explained$r2_per_factor[[1]]) # group 1

```



```{r}
plot_factor_cor(MOFAobject.trained)

```
# by looking at the thiis graph we can tell that there is some corelation among features 

```{r}
plot_variance_explained(MOFAobject.trained, max_r2=15)

```
this is the the total variance between our omics ,  we can tell that "factor 1" explains the most of variation and the rna data is the one that differentiate my samples the most..

```{r}
plot_variance_explained(MOFAobject.trained, plot_total = T)[[2]]

```
here again another proof the the RNA data explaine the most variation among the samples

```{r}
plot_factor(MOFAobject.trained, 
  factor = 1:3,
  color_by = "condition",
)
```
this graph is to capture the influence of the condition  among samples from the first three factors point of wiew , as  we can see it is obvious that factor1 can clearly separate samples into two distinct groups by condition (NORMAL VS TUMOR).
by looking at factor 2 and 3 it becomes less distinct.

```{r}
p = plot_factor(MOFAobject.trained, 
  factors = c(1,2,3),
  color_by = "condition",
  dot_size = 3,        
  dodge = T,          
  legend = F,          
  add_violin = T,      
  violin_alpha = 0.25  
)

p = p + 
  scale_color_manual(values=c("A"="black", "B"="red")) +
  scale_fill_manual(values=c("A"="black", "B"="red"))

print(p)
```


```{r}
plot_weights(MOFAobject.trained,
 view = "rna",
 factor = 1,
 nfeatures = 10,     # Top number of features to highlight
 scale = T           # Scale weights from -1 to 1
)
```
the graph aims to plot RNA features that have to heaviest weights to influence variance , all those genes are considered the most important of all.
the same is applied to the rest of omics data and some features stood out.

```{r}
plot_weights(MOFAobject.trained,
 view = "meth",
 factor = 1,
 nfeatures = 10,     # Top number of features to highlight
 scale = T           # Scale weights from -1 to 1
)
```


```{r}
plot_top_weights(MOFAobject.trained,
 view = "rna",
 factor = 1,
 nfeatures = 10,     # Top number of features to highlight
 scale = T   
 )
```


```{r}
plot_top_weights(MOFAobject.trained,
 view = "prot",
 factor = 1,
 nfeatures = 10,     # Top number of features to highlight
 scale = T           # Scale weights from -1 to 1
)
```


we took as example (NTM) and (CD40) , one of the genes that showed a high wt on varianation , we specified the search to be only on factor 1 since it explains variancse the most , and a clear cut line appeared between samples to emphasize again that these feature's role cannot be ignored in the process of lung cancer incidence 

```{r}
plot_factor(MOFAobject.trained, 
  factors = 1, 
  color_by = "NTM_rna",
  dodge = TRUE,
  add_violin = TRUE)

```


```{r}
plot_factor(MOFAobject.trained, 
  factors = 1, 
  color_by = "CD40_rna",
  dodge = TRUE,
  add_violin = TRUE)
```
upon plotting the gender influence on the tumor formation , it had no clear association . the tumor was almost equally happening to both genders.

```{r}
plot_factor(MOFAobject.trained, 
  factors = 1, 
  color_by = "Gender",
  dodge = TRUE,
  add_violin = TRUE
)
```







```{r}
plot_data_heatmap(MOFAobject.trained, 
  view = "rna",
  factor = 1,  
  features = 25,
  cluster_rows = FALSE, cluster_cols = FALSE,
  show_rownames = TRUE, show_colnames = FALSE,
  scale = "row"
)
```

```{r}
plot_data_heatmap(MOFAobject.trained, 
  view = "meth",
  factor = 1,  
  features = 25,
  cluster_rows = FALSE, cluster_cols = FALSE,
  show_rownames = TRUE, show_colnames = FALSE,
  scale = "row")
```
now we zoomed on factor 1 and drew a heatmap to defferentiate the samples deppending on both RNA and methylation data.
we can conclude that there is a contrast among features.
some are highly up regulated and others down regulated



let's perform an enrichment analysis to figure out which pathways are more involved in lung cancer 






```{r}
weights = get_weights(MOFAobject.trained, as.data.frame = T) 

head(weights , n=3)


```

```{r}
rna_factors = weights %>% filter(view == "rna" & factor == "Factor1")
prot_factors = weights %>% filter(view == "prot" & factor == "Factor1")
meth_factors = weights %>% filter(view == "meth" & factor == "Factor1")
mirna_factors = weights %>% filter(view == "mirna" & factor == "Factor1")


```



```{r}
rna_factors[ ,1 ] = sub("_.*", "", rna_factors[ ,1 ] ) 
prot_factors[ ,1 ] = sub("_.*", "", prot_factors[ ,1 ] )
meth_factors[ ,1 ] = sub("_.*", "",meth_factors[ ,1 ] )


```


```{r}
rna_list = rna_factors$feature
prot_list = prot_factors$feature
meth_list = meth_factors$feature
```

```{r}
#if (!requireNamespace("BiocManager", quietly = TRUE))
 #  install.packages("BiocManager")

#BiocManager::install("msigdbr")
library(msigdbr)
library(fgsea)

```


```{r}
genesets = msigdbr(species = "Homo sapiens", category = "C2", subcategory = "CP:KEGG")

```




```{r}
genesets$gene_symbol =toupper(genesets$gene_symbol)

genesets_rna = genesets[genesets$gene_symbol %in% rna_list ,]


my_list = genesets %>% split(x = .$gene_symbol, f = .$gs_name)
rownames(rna_factors) = rna_factors[ , 1]
rna_factors =rna_factors[ ,-1]
stats = rna_factors[ ,2]
names(stats) = rownames(rna_factors)
eaRes = fgsea(pathways = my_list, stats = stats ,nperm=100)

```



```{r}
ooEA = order(eaRes$pval, decreasing = FALSE)
eaRes=eaRes[ooEA,]
print(head(eaRes))

```


```{r}

topPathwaysUp = eaRes[ES > 0 & pval <.05][head(order(pval), n=10), pathway]
topPathwaysDown = eaRes[ES < 0& pval <.05][head(order(pval), n=10), pathway]
topPathways = c(topPathwaysUp, rev(topPathwaysDown))
plotGseaTable(my_list[topPathways], stats, eaRes, 
              gseaParam=0.5)


```


```{r}
plotEnrichment(my_list[["KEGG_GLYOXYLATE_AND_DICARBOXYLATE_METABOLISM"]],
               stats) + labs(title="KEGG_GLYOXYLATE_AND_DICARBOXYLATE_METABOLISM")
```


```{r}
# Select the necessary columns
gsea_data = eaRes[, c("pathway", "NES", "padj")]

# Convert the FDR q-value to a logarithmic scale
gsea_data$padj = -log10(gsea_data$padj)

# Create a new column to indicate the direction of enrichment
gsea_data$direction = ifelse(gsea_data$NES > 0, "Up", "Down")
```


```{r}
# Create the volcano plot
ggplot(gsea_data, aes(x = NES, y = padj, color = direction , size = abs(NES) )) + 
  geom_point() + 

  theme_classic() + 
  geom_text(aes(label = eaRes$pathway), check_overlap = TRUE, vjust = 3 , size =1.5)+
  
  labs(x = "Normalized Enrichment Score (NES)", 
       y = "-log10(FDR q-value)", 
       color = "Direction",
       size = "NES Absolute Value" ) + 
  scale_color_manual(values = c("Up" = "blue", "Down" = "red")) + 
  theme(legend.position = "bottom")
```




```{r}
# Create a logical vector indicating which rows to combine
rows_to_combine <- eaRes$pathway %in% topPathways

# Combine the matching rows into a single list
combined_list <- eaRes$leadingEdge[rows_to_combine]

# Print the combined list
combined_list

 write.csv( data.frame(combined_list) ,"com" , row.names = F )
```


```{r}
genes_to_search = unlist(combined_list)
```


```{r}
rna_filt = rna[genes_to_search , ]
```



```{r}
library(ComplexHeatmap)
```


```{r}
mycolors= rep("navy",dim(meta)[1])
mycolors[which(meta=="tumor")]="purple"

column_ha = HeatmapAnnotation(Sample_type= meta$condition)
Heatmap(rna_filt, name = "top", top_annotation = column_ha)
Heatmap(rna_filt, name = "top", top_annotation = column_ha, row_names_gp = gpar(fontsize = 2), column_names_gp = gpar(fontsize = 3, mycolors))
```






######################################################################


now for protiens


```{r}

genesets_prot = genesets[genesets$gene_symbol %in% prot_list ,]


my_list_prot = genesets_prot %>% split(x = .$gene_symbol, f = .$gs_name)

stats_prot = prot_factors[ ,3]
names(stats_prot) = prot_factors[ ,1]
eaRes_prot = fgsea(pathways = my_list_prot, stats = stats_prot ,nperm=100)

```



```{r}
ooEA_prot = order(eaRes_prot$pval, decreasing = FALSE)
eaRes_prot=eaRes_prot[ooEA_prot,]
print(head(eaRes_prot))

```


```{r}
topPathwaysUp_prot = eaRes_prot[ES > 0][head(order(pval), n=10), pathway]
topPathwaysDown_prot = eaRes_prot[ES < 0][head(order(pval), n=10), pathway]
topPathways_prot = c(topPathwaysUp_prot, rev(topPathwaysDown_prot))
plotGseaTable(my_list_prot[topPathways_prot], stats_prot, eaRes_prot, 
              gseaParam=0.5)


```




```{r}
# Select the necessary columns
gsea_data_prot = eaRes_prot[, c("pathway", "NES", "padj")]

# Convert the FDR q-value to a logarithmic scale
gsea_data_prot$padj = -log10(gsea_data_prot$padj)

# Create a new column to indicate the direction of enrichment
gsea_data_prot$direction = ifelse(gsea_data_prot$NES > 0, "Up", "Down")
```


```{r}
# Create the volcano plot
ggplot(gsea_data_prot, aes(x = NES, y = padj, color = direction , size = abs(NES) )) + 
  geom_point() + 

  theme_classic() + 
  geom_text(aes(label = eaRes_prot$pathway), check_overlap = TRUE, vjust = 3 , size =1.5)+
  
  labs(x = "Normalized Enrichment Score (NES)", 
       y = "-log10(FDR q-value)", 
       color = "Direction",
       size = "NES Absolute Value" ) + 
  scale_color_manual(values = c("Up" = "blue", "Down" = "red")) + 
  theme(legend.position = "bottom")
```




```{r}
# Create a logical vector indicating which rows to combine
rows_to_combine_prot <- eaRes_prot$pathway %in% topPathways_prot

# Combine the matching rows into a single list
combined_list_prot <- eaRes_prot$leadingEdge[rows_to_combine_prot]

# Print the combined list
combined_list_prot
```


```{r}
prot_to_search = unlist(combined_list_prot)
```



```{r}
prot_filt = prot[rownames(prot) %in% prot_to_search, ]

```


```{r}
library(ComplexHeatmap)
set.seed(123)
mycolors= rep("navy",dim(meta)[1])
mycolors[which(meta=="tumor")]="purple"

column_ha = HeatmapAnnotation(Sample_type= meta$condition)
Heatmap(prot_filt, name = "top", top_annotation = column_ha)
Heatmap(prot_filt, name = "top", top_annotation = column_ha, row_names_gp = gpar(fontsize = 2), column_names_gp = gpar(fontsize = 3, mycolors))
```
########################################################################

pathway analysis for methylation data


```{r}

genesets_meth = genesets[genesets$gene_symbol %in% meth_list ,]


my_list_meth = genesets_meth %>% split(x = .$gene_symbol, f = .$gs_name)

stats_meth = meth_factors[ ,3]
names(stats_meth) = meth_factors[,1]
eaRes_meth = fgsea(pathways = my_list_meth, stats = stats_meth ,nperm=100)

```



```{r}
ooEA_meth = order(eaRes_meth$pval, decreasing = FALSE)
eaRes_meth=eaRes_meth[ooEA_meth,]
print(head(eaRes_meth))

```


```{r}
topPathwaysUp_meth = eaRes_meth[ES > 0][head(order(pval), n=10), pathway]
topPathwaysDown_meth = eaRes_meth[ES < 0][head(order(pval), n=10), pathway]
topPathways_meth = c(topPathwaysUp_meth, rev(topPathwaysDown_meth))
plotGseaTable(my_list_meth[topPathways_meth], stats_meth, eaRes_meth, 
              gseaParam=0.5)


```




```{r}
# Select the necessary columns
gsea_data_meth = eaRes_meth[, c("pathway", "NES", "padj")]

# Convert the FDR q-value to a logarithmic scale
gsea_data_meth$padj = -log10(gsea_data_meth$padj)

# Create a new column to indicate the direction of enrichment
gsea_data_meth$direction = ifelse(gsea_data_meth$NES > 0, "Up", "Down")
```


```{r}
# Create the volcano plot
ggplot(gsea_data_meth, aes(x = NES, y = padj, color = direction , size = abs(NES) )) + 
  geom_point() + 

  theme_classic() + 
  geom_text(aes(label = eaRes_meth$pathway), check_overlap = TRUE, vjust = 3 , size =1.5)+
  
  labs(x = "Normalized Enrichment Score (NES)", 
       y = "-log10(FDR q-value)", 
       color = "Direction",
       size = "NES Absolute Value" ) + 
  scale_color_manual(values = c("Up" = "blue", "Down" = "red")) + 
  theme(legend.position = "bottom")
```




```{r}
# Create a logical vector indicating which rows to combine
rows_to_combine_meth <- eaRes_meth$pathway %in% topPathways_meth

# Combine the matching rows into a single list
combined_list_meth <- eaRes_meth$leadingEdge[rows_to_combine_meth]

# Print the combined list
combined_list_meth
```


```{r}
meth_to_search = unlist(combined_list_meth)
```



```{r}
meth_filt = meth[rownames(meth) %in% meth_to_search, ]

```


```{r}
set.seed(123)
mycolors= rep("navy",dim(meta)[1])
mycolors[which(meta=="tumor")]="purple"

column_ha = HeatmapAnnotation(Sample_type= meta$condition)
Heatmap(meth_filt, name = "top", top_annotation = column_ha)
Heatmap(meth_filt, name = "top", top_annotation = column_ha, row_names_gp = gpar(fontsize = 2), column_names_gp = gpar(fontsize = 3, mycolors))
```




```{r}
common_down_pathways <- topPathwaysDown[topPathwaysDown %in% topPathwaysDown_prot ]


```


```{r}
common_up_pathways1 <- topPathwaysUp[topPathwaysUp %in% topPathwaysUp_prot]

```



```{r}
common_up_pathways2 <- topPathwaysUp[topPathwaysUp %in% topPathwaysUp_meth]

```




```{r}
plotEnrichment(my_list[["KEGG_CALCIUM_SIGNALING_PATHWAY"]],
              
               stats) + labs(title="KEGG_CALCIUM_SIGNALING_PATHWAY")

```


```{r}
plotEnrichment(my_list[["KEGG_CALCIUM_SIGNALING_PATHWAY"]],
              
               stats_prot) + labs(title="KEGG_CALCIUM_SIGNALING_PATHWAY")

```

```{r}
plotEnrichment(my_list[["KEGG_CALCIUM_SIGNALING_PATHWAY"]],
              
               stats_meth) + labs(title="KEGG_CALCIUM_SIGNALING_PATHWAY")

```


####################################


```{r}
eaRes_top_rna = eaRes[   eaRes$pathway %in% topPathways  , ]
```


```{r}

total = sapply(eaRes_top_rna$leadingEdge, length)

```



```{r}
eaRes_top_rna$overlap = total
```

```{r}
library(dplyr)

eaRes_top_rna <- eaRes_top_rna %>% 
  mutate(hits = overlap / size)
```


```{r}

eaRes_top_rna %>%
  arrange(desc(hits)) %>%
  ggplot(aes(x = pval, y = size, color = NES, size = hits)) + 
  geom_point() + 
  geom_text(aes(label = pathway), check_overlap = TRUE, vjust = 1 ,size =2) + 
  scale_colour_gradient(low = "green", high = "red", name = "NES Score") + 
  scale_size(range = c(1, 5)) + 
  labs(x = "pval", y = "size", title = "Top 20 Pathways by Adjusted P-value") + 
  theme(axis.text.x = element_text(angle =54, hjust = 1, vjust = 0.5, size =8 ))
```


```{r}
topPathways
```

```{r}
up_meth  = eaRes_meth[ES > 0][order(pval) , pathway]
down_meth = eaRes_meth[ES < 0][order(pval), pathway]

up_rna  = eaRes[ES > 0][order(pval) , pathway]
down_rna = eaRes[ES < 0][order(pval), pathway]

up_prot  = eaRes_prot[ES > 0][order(pval) , pathway]
down_prot = eaRes_prot[ES < 0][order(pval), pathway]
```

```{r}
common_rna_prot = up_rna[ up_rna %in% up_prot]
```

```{r}
common_all_up = up_rna[ up_meth %in% up_prot]
common_all_down = down_rna [ down_meth %in% down_prot]
```
```{r}

# Filtering the data frame based on common pathways that are upregulated
eaRes_up_common <- eaRes[eaRes$pathway %in% common_all_up, ]
```

```{r}
up_genes_down_epi = common_rna_prot[common_rna_prot %in% down_meth ]
```
```{r}
eaRes_up_genes_down_epi = eaRes[eaRes$pathway %in% up_genes_down_epi, ]

```
```{r}

# Sample Data
pathways          <- eaRes_up_genes_down_epi$pathway
enrichment_scores <- eaRes_up_genes_down_epi$NES
p_values          <- eaRes_up_genes_down_epi$pval

# Data Frame
df <- data.frame(Pathway = pathways, 
                 Enrichment_Score = enrichment_scores, 
                 P_Value = p_values)
#  Bubble Plot
ggplot(df, aes(x = Enrichment_Score, y = -log10(P_Value), size = Enrichment_Score, color = P_Value, label = Pathway)) +
  geom_point(alpha = 0.7) +  # Adjust transparency
  scale_size_continuous(range = c(3, 10)) +  # Adjust bubble size range
  scale_color_gradient(low = "blue", high = "red") +  # Gradient color scale
  geom_text_repel(size = 2.5, box.padding = 0.5, point.padding = 0.5, segment.color = 'grey50') +  # Add labels
  labs(title = "Pathway Enrichment and Significance",
       x = "Enrichment Score",
       y = "-log10(P-Value)",
       size = "Enrichment Score",
       color = "P-Value") +
  theme_minimal() +  # Minimal theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  

```
```{r}

plotEnrichment(my_list[["KEGG_RIBOSOME"]],
              
               stats_meth) + labs(title="KEGG_RIBOSOME from the methylation data view")

```


```{r}
plotEnrichment(my_list[["KEGG_RIBOSOME"]],
              
               stats) + labs(title="KEGG_RIBOSOME from the rna data view")
```

```{r}
plotEnrichment(my_list[["KEGG_RIBOSOME"]],
              
               stats_prot) + labs(title="KEGG_RIBOSOME from the proteins data view")
```
```{r}
KEGG_RIBOSOME_genes <- eaRes$leadingEdge[eaRes$pathway %in% "KEGG_RIBOSOME"]


```



```{r}
# Example fgsea results data frame
fgsea_res <- data.frame(
  pathway = eaRes_up_genes_down_epi$pathway,
  NES = eaRes_up_genes_down_epi$NES,  # Normalized Enrichment Score
  pval = eaRes_up_genes_down_epi$pval  # P-values
)


threshold <- 0.5  # Define a threshold for similarity

# Create a data frame with pathway relationships
pathway_pairs <- expand.grid(pathway1 = fgsea_res$pathway, pathway2 = fgsea_res$pathway) %>%
  filter(pathway1 != pathway2) %>%
  rowwise() %>%
  mutate(similarity = abs(fgsea_res$NES[which(fgsea_res$pathway == pathway1)] - 
                          fgsea_res$NES[which(fgsea_res$pathway == pathway2)])) %>%
  filter(similarity <= threshold) %>%
  select(pathway1, pathway2, similarity)

# Rename columns for clarity
colnames(pathway_pairs) <- c("from", "to", "weight")

```



```{r}
library(RCy3)
cytoscapePing()

```





```{r}
sessionInfo()


```




